\documentclass[finalReport.tex]{subfiles}
\begin{document}
\chapter{Teamwork}\label{ch:team}

The team developed the project by splitting up into sub-teams: as mentioned above, one team was focussing on the Android client, the other was working on the Python server and client. 

A number of different forms of communication have been used, according to what was outlined in the initial report. \textit{WhatsApp} and \textit{Skype} were the main platforms used for communication, allowing team members to stay in touch and update them with individual project progress. 

The team met weekly to discuss the project, and development meetings were held where the team would work together to tackle specific aspects of the project, especially during the initial and the last phases of the work.

\textit{Git} was a tool used for the development of the application. \textit{GitHub}'s feature branches were used to allow team members to work on different parts of the system. The following branches were made in addition to the default, the master one:
\begin{itemize}
\item \textbf{android:} development of the Android application
\item \textbf{develop:} development of the Python application
\item\textbf{backend:} development of the Python server and Python client
\item \textbf{ui:} implementation of the Python GUI
\item \textbf{deliverables:} deliverables of the project, the initial report and the final report.
\end{itemize}
 
When changes had to be made, a procedure was in place which was followed by the team members. This involved members having to make pull requests on the branches they were working on and then having these requests approved by the Git coordinator.


\end{document}